Skills, Practices, and Aspirations \\ of Small-scale Entrepreneurs \\ in Low-income Settings

### 2021-02-07 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Added tweaks to the referencs and to the appendix

\documentclass[hideothersubsections, usenames,dvipsnames,11pt]{beamer}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amsmath}
\usepackage{mathpazo}
\usepackage{hyperref}
\usepackage{multimedia}
\usepackage{multicol}
\usepackage{epsfig}
\usepackage{curves}
\usepackage{epsfig}
\usepackage{epic}
\usepackage{curves}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{multicol}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{fix-cm}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{natbib}

@@

\usetheme[right]{Berkeley}
\setbeamercolor{background canvas}{bg=offwhite}
\setbeamercolor{palette primary}{bg=cerulean,fg=white}
\setbeamercolor{palette secondary}{bg=bdf,fg=white}
\setbeamercolor{frametitle}{fg=offwhite}
%\setbeamercolor{sidebar}{bg=cerulean}
%\newenvironment{transitionframe}{\setbeamercolor{background canvas}{bg=bdf}\begin{frame}}{\end{frame}}
%\setbeamercolor{title}{fg=black}
%\setbeamercolor{itemize item}{fg=blue}
%\setbeamercolor{itemize subitem}{fg=blue}
%\setbeamercolor{enumerate item}{fg=blue}
%\setbeamercolor{enumerate subitem}{fg=blue}
%\setbeamercolor{button}{bg=offwhite,fg=blue}

% Create subsection transitions without subsection numbering
\def\subsectionname{\translate{Subsection}}
\def\insertsubsectionnumber{\arabic{subsection}}
\setbeamertemplate{subsection page}
{
  %\begin{centering}
    %{\usebeamerfont{subsection name}\usebeamercolor[fg]{subsection name}\subsectionname~\insertsubsectionnumber}
    %\vskip1em\par
    \begin{beamercolorbox}[sep=14pt,center]{part title}
      \setbeamerfont{subsection title}{size=\fontsize{14}{20}\selectfont}
      \usebeamerfont{subsection title}\insertsubsection\par
    \end{beamercolorbox}
  %\end{centering}
}
\def\subsectionpage{\usebeamertemplate*{subsection page}}
\AtBeginSubsection
{\frame{\subsectionpage}}

% Font
\usefonttheme{serif}
\setbeamercovered{invisible}
\setbeamerfont{section in sidebar}{size=\fontsize{5.3}{5}\selectfont}
\setbeamerfont{subsection in sidebar}{size=\fontsize{4.4}{5.5}\selectfont}
%\setbeamerfont{subsubsection in sidebar}{size=\fontsize{4}{7}\selectfont}
\setbeamerfont{title in sidebar}{}
\setbeamerfont{author in sidebar}{}
\setbeamercolor{section in sidebar}{bg=bdf,fg=offwhite}
\setbeamercolor{subsection in sidebar}{bg=bdf,fg=offwhite}
\linespread{1.25}

%\setbeamercolor{title}{bg=red!25!blue,fg=white}
%\setbeamercolor{fo} {bg=red!25!blue,fg=white}
%\setbeamercolor{sidebar}{bg=red!25!blue,fg=white}
%\setbeamercolor{author in sidebar}{fg=black!20!white}
%\setbeamercolor{title in sidebar}{fg=white}
%\setbeamercolor{normal text}{bg=white}
%\setbeamercolor{frametitle}{fg=white}
%\setbeamercolor{section in sidebar}{bg=black,fg=white}
%\setbeamercolor{subsection in sidebar}{bg=black,fg=white}
%\setbeamercolor{block title}{bg=red!25!blue,fg=white}
%\setbeamercolor{block body}{bg=blue!20!white,fg=black}
%\setbeamerfont{subsection in sidebar}{size=\tiny}
%\setbeamerfont{title in sidebar}{size=\scriptsize}
%\setbeamerfont{author in sidebar}{size=\tiny}
%\setbeamercovered{transparent}
\setbeamerfont{itemize/enumerate body}{size={\fontsize{9.5}{9.5}}}
\setbeamerfont{itemize/enumerate subbody}{size={\fontsize{8}{8}}}
%\setbeamerfont{itemize/enumerate subbody}{family=\sffamily}

@@

% Create generic TOC

%\AtBeginSection
%{\begin{frame}{Overview}
%\tableofcontents[currentsection,hideothersubsections]
%\end{frame}}

@@

\begin{frame}
\frametitle{Business Practices of Small Firms}
	\citet{McKenzie2017} identify set of XX practices most closely associated with business performance
	\begin{itemize_2pt}
		\item Example practices:
		\begin{itemize_2pt}
			\item 
			\item 
			\item 
			\item 
			\item 
		\end{itemize_2pt}
	\item Does adoption of "best practices" \emph{cause} increase in performance?
	\item How can practice adoption best be facilitated?
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Evidence on Impact}
	\begin{itemize_2pt}
	\item First wave (Karlan and Valdivia, 2011, Field, et al., 2010; Bruhn \& Zia, 2013; Bulte et al., 2017; Anderson, Chandy, and Zia, 2018)
					 \citep{Karlan2011} \citep{Field2010} \citep{Bruhn2013} \citep{Bulte2017} \citep{Anderson2018}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Evidence on Impact}
	\begin{itemize_2pt}
	\item Econometric and implementation issues \citep{McKenzie2014}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Evidence on Impact}
	\begin{itemize_2pt}
	\item Recent evaluations (McKenzie, 2020) \citep{McKenzie2020}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

	\citet{Anderson2018} assign 852 South African businesses to two distinct trainings:
	\begin{enumerate_2pt}
		\item Finance/accounting skills
		\item Marketing/sales skills
	\end{enumerate_2pt}

@@

	\citet{Anderson2018} assign 852 South African businesses to two distinct trainings:
	\begin{enumerate_2pt}
		\item Finance/accounting skills
		\begin{itemize_2pt}
			\item Increased profits
			\item "Efficiency focus" on lower costs
			\item[] $\rightarrow$ Benefits established businesses (less market exposure)
		\end{itemize_2pt}
		\item Marketing/sales skills
		\begin{itemize_2pt}
			\item Increased profits
			\item "Growth focus" on higher sales, stock investments, and hiring
			\item[] $\rightarrow$ Benefits new businesses (less market exposure)
		\end{itemize_2pt}
	\end{enumerate_2pt}

@@

\begin{frame}
\frametitle{Training Specific Domain}
	\begin{itemize_2pt}
	\item \citep{Anderson2018}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Imprecision of Outcome Measures}
	\begin{itemize_2pt}
	\item Confidence Intervals, pic?
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Reliability of Self-reports}
	\begin{itemize_2pt}
	\item Self-reports of aggregate \citep{deMel2009}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Reliability of Self-reports}
	\begin{itemize_2pt}
	\item Disaggregating quantities in self-reports \citep{deMel2009}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Reliability of Self-report}
	\begin{itemize_2pt}
	\item Direct measures \citep{deMel2009}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

%
\begin{frame}
\frametitle{Disseminating Knowledge}
		\begin{itemize_2pt}
		\item \textcolor{bdf}{Handbook}
			\begin{itemize_2pt}
			\item \textcolor{bdf}{Pure information}: Which practices, how to adopt, and why?\\
            %\item \textcolor{bdf}{Positive Frame}: Retailers who implement [x] report y\% \textcolor{bdf}{higher} sales and z\% \textcolor{bdf}{higher} profits.
            %\item \textcolor{bdf}{Negative Frame}: Retailers who do \textcolor{bdf}{not} implement [x] report y\% \textcolor{bdf}{lower} sales and z\% \textcolor{bdf}{lower} profits.
			\end{itemize_2pt}
\bigskip
Supplemented with two types of experiential learning:
\bigskip
		\item \textcolor{bdf}{Movie}
			\begin{itemize_2pt}
			\item \textcolor{bdf}{Psychological and emotional involvement}$\rightarrow$ social learning is possible through \textcolor{bdf}{observing the successful experience of similar others}.
			\item Bernard, et al. (2014); La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013).\\
			\end{itemize_2pt}

\bigskip
		\item \textcolor{bdf}{On-site Assistance}
			\begin{itemize_2pt}
			\item \textcolor{bdf}{Hands-on involvement} $\rightarrow$ social learning is possible through own \textcolor{bdf}{experience, with a small nudge} (Kolb, 1984).
			\item Facilitated by local lay person
			\end{itemize_2pt}
			\vspace{0.05in}
%\bigskip
%			$\rightarrow$ Horse race between role models and business counseling.
		\end{itemize_2pt}

@@

\begin{frame}
\frametitle{Research Questions}
	\begin{itemize_2pt}
	%\item \textcolor{bdf}{Local characterization}
	%\vspace{0.05in}
	%	\begin{itemize_2pt}
	%	\item Which practices are associated with high profits?
	%	\item How do successful businesses implement them?
	%	\end{itemize_2pt}
	%\vspace{0.05in}
	\item \textcolor{bdf}{Adoption}
		\begin{itemize_2pt}
		\item Do retailers adopt these practices once peer best practices are aggregated and made common knowledge?
		\item If so, ...
			\begin{itemize_2pt}
			\item Does the type of experiential involvement matter?
			\end{itemize_2pt}
		\end{itemize_2pt}
    \vspace{0.3in}
	\item \textcolor{bdf}{Impact}
		\begin{itemize_2pt}
		\item Does firm profitability increase?
		\item If so, what are the channels?
		\end{itemize_2pt}
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Sample}
\begin{itemize_2pt}
\item Listing of 2042 small retail businesses from 29 administrative communities (Kelurahan) in urban Jakarta
\item Selection criteria for firm listing:
	\begin{itemize_2pt}
%	\item General willingness to grow
	\item At least 4$m^{2}$ in size
	\item At least two different product categories on offer
	\item At least 30 meters distance to next business in sample $\rightarrow$ to minimize spillovers
	\end{itemize_2pt}
\item Random sample of 1301 from the list
\item Randomization to treatment arms stratified by
	\begin{itemize_2pt}
	\item Gender
	\item Firm space (4-6$m^2$, 6-10$m^2$, 10 and above $m^2$)
	\item Composite score of business practices above or below median
	\item Kelurahan
	\end{itemize_2pt}
\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Experimental Design}
	\begin{itemize_2pt}
%    \item \textcolor{bdf}{Same set of business practices} across treatments \\
	\item Three types of information provision:
	\vspace{0.05in}
		\begin{itemize_2pt}
		\item \textcolor{bdf}{Handbook} with best practices and tips
		\item \textcolor{bdf}{Movie} with successful peers
		\item Best-practice on-site implementation \textcolor{bdf}{assistance}
		\end{itemize_2pt}
	\vspace{0.05in}
\end{itemize_2pt}
	\begin{itemize_2pt}
\item{Five experimental groups}
        %\begin{itemize_2pt}
        %\item{Handbooks (N=1040)}
        %: Positive Framing (N=520) and Negative Framing (N=520)}\\
	\vspace{0.05in}
            \begin{enumerate_2pt}
              \item \textcolor{bdf}{Handbook} only (N=260)
              \item \textcolor{bdf}{Handbook} and invitation to \textcolor{bdf}{movie} screening (N=260)
              \item \textcolor{bdf}{Handbook} and offer of two \textcolor{bdf}{assistance} visits (N=260)
              \item \textcolor{bdf}{Handbook} and both \textcolor{bdf}{movie} and \textcolor{bdf}{assistance} (N=260)
              \item Control (N=261)
            \end{enumerate_2pt}
        \end{itemize_2pt}
    %\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Summary Statistics}
{\tiny{
	\begin{table}
		%\begin{adjustbox}{width=9.6cm}
		\centering	
		%\tabcolsep=0.2cm

@@

	\end{table}}}
\begin{itemize_2pt}
\item Test of Joint Orthoganality from Multinomial Logit (P-value): 0.857
\end{itemize_2pt}
\end{frame}

@@

	\item[] $\rightarrow$ \textcolor{bdf}{Non-record-keeping practices}
	\item[] $\rightarrow$ Causal-mediation analysis: \textcolor{bdf}{Stocking up and marketing practices} drive performance effects
	\item[] $\rightarrow$ Variance in profits among treated firms does not converge
	\item[] $\rightarrow$ \textcolor{bdf}{Efficiency gains}
\end{itemize_2pt}
\end{frame}

@@

We directly measure business aspirations .. 
\begin{itemize_2pt}
	\item .. at baseline, midline, and endline
	\item .. for short (one year) and long ("ideal business") time horizons
	\item .. for various dimensions of potential business expansion
    \begin{itemize_2pt}
   		\item Sales on a normal day
    	\item Physical size
   		\item Customers on a normal day
    	\item Employees
    \end{itemize_2pt}
\item[] $\rightarrow$ \textcolor{bdf}{No impact on aspirations}
\item[] $\rightarrow$ Performance likely driven by increase in \textcolor{bdf}{business knowledge}
\end{itemize_2pt}

@@

@@

\subsection*{References}
\begin{frame}[allowframebreaks]
\frametitle{References}

\bibliographystyle{econometrica}
\bibliography{SME_library}
\end{frame}

>>>>

\documentclass[hideothersubsections, usenames,dvipsnames,11pt]{beamer}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{curves}
\usepackage{epic}
\usepackage{epsfig}
\usepackage{fix-cm}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{mathpazo}
\usepackage{multimedia}
\usepackage{multicol}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{tikz}

@@

\usetheme[right]{Berkeley}
\setbeamercolor{background canvas}{bg=offwhite}
\setbeamercolor{palette primary}{bg=cerulean,fg=white}
\setbeamercolor{palette secondary}{bg=bdf,fg=white}
\setbeamercolor{frametitle}{fg=offwhite}
%\setbeamercolor{sidebar}{bg=cerulean}
%\newenvironment{transitionframe}{\setbeamercolor{background canvas}{bg=bdf}\begin{frame}}{\end{frame}}
%\setbeamercolor{title}{fg=black}
%\setbeamercolor{itemize item}{fg=blue}
%\setbeamercolor{itemize subitem}{fg=blue}
%\setbeamercolor{enumerate item}{fg=blue}
%\setbeamercolor{enumerate subitem}{fg=blue}
%\setbeamercolor{title}{bg=red!25!blue,fg=white}
%\setbeamercolor{fo} {bg=red!25!blue,fg=white}
%\setbeamercolor{sidebar}{bg=red!25!blue,fg=white}
%\setbeamercolor{author in sidebar}{fg=black!20!white}
%\setbeamercolor{title in sidebar}{fg=white}
%\setbeamercolor{normal text}{bg=white}
%\setbeamercolor{frametitle}{fg=white}
%\setbeamercolor{section in sidebar}{bg=black,fg=white}
%\setbeamercolor{subsection in sidebar}{bg=black,fg=white}
%\setbeamercolor{block title}{bg=red!25!blue,fg=white}
%\setbeamercolor{block body}{bg=blue!20!white,fg=black}
%\setbeamerfont{subsection in sidebar}{size=\tiny}
%\setbeamerfont{title in sidebar}{size=\scriptsize}
%\setbeamerfont{author in sidebar}{size=\tiny}
%\setbeamercovered{transparent}
\setbeamercolor{section in sidebar}{bg=bdf,fg=offwhite}
\setbeamercolor{subsection in sidebar}{bg=bdf,fg=offwhite}
\setbeamercolor{button}{bg=bdf,fg=offwhite}

% Create subsection transitions without subsection numbering
\def\subsectionname{\translate{Subsection}}
\def\insertsubsectionnumber{\arabic{subsection}}
\setbeamertemplate{subsection page}
{
  %\begin{centering}
    %{\usebeamerfont{subsection name}\usebeamercolor[fg]{subsection name}\subsectionname~\insertsubsectionnumber}
    %\vskip1em\par
    \begin{beamercolorbox}[sep=14pt,center]{part title}
    	%\setbeamercolor{box1}{fg=yellow, bg=yellow}
    	\setbeamerfont{subsection title}{size=\fontsize{14}{20}\selectfont}
    	\usebeamerfont{subsection title}\insertsubsection\par
    \end{beamercolorbox}
  %\end{centering}
}
\def\subsectionpage{\usebeamertemplate*{subsection page}}
\AtBeginSubsection
{\frame{\subsectionpage}}

% Font
\usefonttheme{serif}
\setbeamercovered{invisible}
\setbeamerfont{section in sidebar}{size=\fontsize{5.3}{5}\selectfont}
\setbeamerfont{subsection in sidebar}{size=\fontsize{4.4}{5.5}\selectfont}
%\setbeamerfont{subsubsection in sidebar}{size=\fontsize{4}{7}\selectfont}
\setbeamerfont{title in sidebar}{}
\setbeamerfont{author in sidebar}{}
\setbeamerfont{itemize/enumerate body}{size={\fontsize{9.5}{9.5}}}
\setbeamerfont{itemize/enumerate subbody}{size={\fontsize{8}{8}}}
%\setbeamerfont{itemize/enumerate subbody}{family=\sffamily}
\setbeamerfont{button}{size={\fontsize{8}{8}}}
\linespread{1.25}

@@

@@

\begin{frame}
\frametitle{Business Practices of Small Firms}
	\citet{McKenzie2017} identify set of XX practices most closely associated with business performance
	\begin{itemize_2pt}
		\item Example practices:
		\begin{itemize_2pt}
			\item 
			\item 
			\item 
			\item 
			\item 
		\end{itemize_2pt}
	\end{itemize_2pt}

\vspace{0.1in}

	Open questions
	\begin{itemize_2pt}
		\item Does adoption of "best practices" \emph{cause} performance to increase?
		\item How can adoption of practices best be encouraged?
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Evidence of Impact}
	\begin{itemize_2pt}
	\item First wave (Karlan and Valdivia, 2011, Bruhn and Zia, 2013; Giné and Mansuri, 2014; Field, et al., 2010; Bulte et al., 2017; Anderson, Chandy, and Zia, 2018)
					 \citep{Karlan2011} \citep{Field2010} \citet{Gine2014} \citep{Bruhn2013} \citep{Bulte2017} \citep{Anderson2018}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Evidence of Impact}
	\begin{itemize_2pt}
	\item Econometric and implementation issues \citep{McKenzie2014}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}[label=McK2020_profits]
\frametitle{Evidence of Impact}

	Including more recent evaluations \citep{McKenzie2020}

\vspace{-0.5em}

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=21.5em]{pics/McK2020_profits.png}
		\label{McKenzie(2020): Profits}
	\end{figure}

	\vspace{-1em}

	\begin{itemize_2pt}
		\item Small positive impact on practice adoption, profits, and \hyperlink{McK2020_sales}{\beamergotobutton{sales}}
	\end{itemize_2pt}

	%Right side pics
	%\begin{tikzpicture}[remember picture, overlay]
		%\node[shift={(-6.5em,1em)}]() at (current page.south east){%
		%\hyperlink{appendix_sales}{\beamergotobutton{Sales}}};        
	%\end{tikzpicture}

@@

	\citet{Anderson2018} assign 852 South African MSEs to distinct types of training:
	\begin{enumerate_2pt}
		\item Marketing/sales skills
		\item[]
		\item[]
		\item Finance/accounting skills
		\item[]
		\item[]
	\end{enumerate_2pt}

@@

	\citet{Anderson2018} assign 852 South African businesses to two distinct trainings:
	\begin{enumerate_2pt}

		\item Marketing/sales skills
		\begin{itemize_2pt}
			\item 61\% increase in profits
			\item "Growth focus" on higher sales, stock investments, and hiring
			\item[] $\rightarrow$ Benefits new businesses ($=$ less market exposure)
		\end{itemize_2pt}

		\item Finance/accounting skills

		\begin{itemize_2pt}
			\item 41\% increase in profits
			\item "Efficiency focus" on lower costs
			\item[] $\rightarrow$ Benefits established businesses
		\end{itemize_2pt}

		\item[] $\rightarrow$ Different "pathways to profits" (title of the paper)

	\end{enumerate_2pt}

@@

@@

\begin{frame}
\frametitle{Imprecision of Outcome Measures}

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=23.5em]{pics/McK2020_profits.png}
		\label{McKenzie(2020): Profits}
	\end{figure}

\vspace{-1em}

	\begin{itemize_2pt}
		\item \textcolor{bdf}{Extremely wide confidence intervals} on impact estimates
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Self-reports and aggregation}
	\begin{itemize_2pt}
	\item Self-reports of aggregate \citep{deMel2009}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Self-reports and aggregation}
	\begin{itemize_2pt}
	\item Disaggregating quantities in self-reports \citep{deMel2009}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Self-reports and aggregation}
	\begin{itemize_2pt}
	\item Direct measures \citep{deMel2009}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Disseminating Knowledge}

	Basic information intervention
	\begin{itemize_2pt}
		\item \textcolor{bdf}{Handbook}
		\begin{itemize_2pt}
			\item \textcolor{bdf}{Pure information}: Which practices, how to adopt, and why?\\
		\end{itemize_2pt}
	\end{itemize_2pt}

	\vspace{1.0em}

	Two complementary behavioral interventions:
	\begin{itemize_2pt}
		\item \textcolor{bdf}{Movie}
		\begin{itemize_2pt}
			\item \textcolor{bdf}{Psychological and emotional involvement}$\rightarrow$ social learning is possible through \textcolor{bdf}{observing the successful experience of similar others}.
			\item Bernard, et al. (2014); La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013).\\
		\end{itemize_2pt}

		\item \textcolor{bdf}{On-site Assistance}
			\begin{itemize_2pt}
				\item \textcolor{bdf}{Hands-on involvement} $\rightarrow$ social learning is possible through own \textcolor{bdf}{experience, 					with a small nudge} (Kolb, 1984).
				\item Facilitated by local lay person
			\end{itemize_2pt}

	\end{itemize_2pt}

@@

\begin{frame}
\frametitle{Research Questions}

	\textcolor{bdf}{Characterization of local best practices}
	\begin{itemize_2pt}
		\item Which practices are associated with high profits?
		\item How do successful businesses implement them?
	\end{itemize_2pt}
	\vspace{1.0em}

	\textcolor{bdf}{Adoption of best practices}
	\begin{itemize_2pt}
		\item Do retailers adopt these practices once peer best practices are aggregated and made common knowledge?
		\item If so, does the type of experiential involvement matter?

	\end{itemize_2pt}
    \vspace{1.0em}

	\textcolor{bdf}{Impact on business performance}
	\begin{itemize_2pt}
		\item Does firm profitability increase?
		\item If so, what are the channels?
	\end{itemize_2pt}

@@

\begin{frame}
\frametitle{Sample}
\begin{itemize_2pt}
\item Listing of 2042 small retail businesses from 29 sub-districts ("kelurahan") in urban Jakarta
\item Selection criteria for firm listing:
	\begin{itemize_2pt}
%	\item General willingness to grow
	\item At least 4$m^{2}$ in size
	\item At least two different product categories on offer
	\item At least 30 meters distance to next business in sample $\rightarrow$ to minimize spillovers
	\end{itemize_2pt}
\item Random sample of 1301 from the list
\item Randomization to treatment arms stratified by
	\begin{itemize_2pt}
	\item Gender
	\item Firm space (4-6$m^2$, 6-10$m^2$, 10 and above $m^2$)
	\item Composite score of business practices above or below median
	\item Sub-district
	\end{itemize_2pt}
\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Experimental Design}

	Three types of information delivery:
		\begin{enumerate_2pt}
			\item \textcolor{bdf}{Handbook} with best practices and implementation tips
			\item \textcolor{bdf}{Movie} with successful peers
			\item \textcolor{bdf}{On-site assistance} with practice adoption
			\item[] $\rightarrow$ Movie, assistance exclusively based on handbook
		\end{enumerate_2pt}
	\vspace{0.1in}

	Five experimental groups
    	\begin{enumerate_2pt}
        	\item \textcolor{bdf}{Handbook} only (N=260)
        	\item \textcolor{bdf}{Handbook} + invitation to \textcolor{bdf}{movie} screening (N=260)
        	\item \textcolor{bdf}{Handbook} + offer of two \textcolor{bdf}{assistance} visits (N=260)
        	\item \textcolor{bdf}{Handbook} + \textcolor{bdf}{movie} + \textcolor{bdf}{assistance} (N=260)
       		\item Control (N=261)
      	\end{enumerate_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Summary Statistics}

%\makebox[\linewidth][c]{
%\begin{tabular}{l cc ddd}

{\tiny{
	\begin{table}
		%\begin{adjustbox}{width=9.6cm}
		\centering	
		\tabcolsep=0.2cm

@@

	\end{table}}}
%\end{tabular}
%\begin{itemize_2pt}
%\item Test of Joint Orthoganality from Multinomial Logit (P-value): 0.857
%\end{itemize_2pt}
\end{frame}

@@

	\item[] $\rightarrow$ \textcolor{bdf}{Non-record-keeping practices}
	\item[] $\rightarrow$ \textcolor{bdf}{Stocking up and marketing practices} appear to drive performance effects (causal-mediation analysis)
	\item[] $\rightarrow$ Variance in profits among treated firms does not converge
	\item[] $\rightarrow$ \textcolor{bdf}{Efficiency gains}
\end{itemize_2pt}
\end{frame}

@@

\pause
\vspace{1.0em}

We directly measure \textcolor{bdf}{business aspirations} .. 
\begin{itemize_2pt}
	\item .. at baseline, midline, and endline
	\item .. for short (one year) and long ("ideal business") time horizons
	\item .. for various dimensions of potential business expansion
    \begin{itemize_2pt}
   		\item Sales on a normal day
    	\item Physical size
   		\item Customers on a normal day
    	\item Employees
    \end{itemize_2pt}
\item[] $\rightarrow$ \textcolor{bdf}{No impact on aspirations}
\item[] $\rightarrow$ Performance likely driven by increase in \textcolor{bdf}{business knowledge}
\end{itemize_2pt}

@@

-----

%\addtocontents{toc}{\protect\setcounter{tocdepth}{0}}

\begin{frame}[label=references, allowframebreaks]
\frametitle{References}
\bibliographystyle{econometrica}
\bibliography{SME_library}
\end{frame}

@@

\begin{frame}{Appendix Overview}
\tableofcontents[currentsection,hideothersubsections]
\end{frame}

\begin{frame}[label=McK2020_sales]
\frametitle{Evidence of Impact}

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=23.2em]{pics/McK2020_sales.png}
		\label{McKenzie(2020): Sales}
	\end{figure}

	\vspace{-1em}

	\begin{itemize_2pt}
		\item Small positive impact on sales (back to \hyperlink{McK2020_profits}{\beamergotobutton{profits}})
	\end{itemize_2pt}
